\begin{frame}

\frametitle{Reading Material}

\footnotesize

Academic:

\begin{itemize}

\item Tom Mens and Tom Tourw\'e. 2004. \emph{A Survey of Software Refactoring}.
IEEE Transactions on Software Engineering 30 (2), 2004, 126--139.

\end{itemize}

Web:

\begin{itemize}

\item Shvets Group, et al. \url{https://refactoring.guru/}

\begin{itemize}

\item \footnotesize \url{https://refactoring.guru/catalog/}.

\end{itemize}

\item Martin Fowler, \url{http://refactoring.com/}

\begin{itemize}

\item \footnotesize \url{http://refactoring.com/catalog/}.

\end{itemize}

\end{itemize}

Light reading:

\begin{itemize}

\item \texttt{oleks} \& \texttt{br0ns}. \emph{Unix-Like Data Processing
Utilities}. 2015. \url{http://atu15.onlineta.org/unix-like-data-processing.pdf}

\end{itemize}

\end{frame}


\begin{frame}

\frametitle{Video Material}

\footnotesize

\begin{itemize}

\item Martin Fowler. \emph{Workflows of Refactoring}. OOP2014.
\url{https://youtu.be/vqEg37e4Mkw}.

\item Ben Orenstein. \emph{Refactoring from Good to Great}. Aloha Ruby Conf
2012. \url{https://youtu.be/DC-pQPq0acs}

\item Joshua Bloch. \emph{How To Design A Good API and Why It Matters}. Google
Tech Talks 2007. \url{https://youtu.be/aAb7hSCtvGw}.

\item Robert C. Martin. \emph{SOLID Principles of Object Oriented \& Agile
Design}. Yale, 2014. \url{https://youtu.be/QHnLmvDxGTY}.

% Rigidity
% Fragility
% Non-reusability

\end{itemize}

\end{frame}


\begin{frame}

\frametitle{Summer Reading}

\footnotesize

\begin{itemize}

\item Robert C. Martin. \emph{Clean Code: A Handbook of Agile Software
Craftsmanship}. Prentice Hall, 2008.

\end{itemize}

\end{frame}
